\chapter{Technologies}
\label{ch:Technologies}
\section{MANO Frameworks}
\label{manoframeworks}
In this section, a few MANO frameworks and their NSD schemata are listed(list of a few parameters and their description). Among several frameworks, the plan is to select a few and set them up locally, deploy network services and support them in the project. This list is subjected to future additions or removals.

\subsection{Pishahang}
\label{SecSONATA}
Pishahang is a framework consolidated from state-of-the-art NFV and Cloud management and orchestration tools and technologies. Pishahang is a framework for jointly managing and orchestrating virtual network functions and cloud-based microservices. 

Pishahang deploys, manages and orchestrates complex services by consolidating and extending current Cloud and NFV tools and technologies \cite{kouchaksaraei2018pishahang}.

\subsubsection{Network Service Descriptor Section}
    \begin{table}[h]
    \centering
    \begin{tabular}{ |p{4cm}|p{10cm}|}
        \hline
        \textbf{Parameter} & \textbf{Description} \\
        \hline
         
         Vendor & Identifies the network service uniquely across all network service vendors. \\
         \hline
         Name & Name of the network service without its version. \\
         \hline
         Version & Names the version of the NSD. \\
         \hline
         Author & It's an optional parameter. It describes the author of NSD \\
         \hline
         Description & It's an optional parameter, provides an arbitrary description of the network service. \\
         \hline
    \end{tabular}
    \caption{Pishahang: Network Service Descriptor Section}
    \label{tab:SONATA_general_section}
\end{table}
\pagebreak
\subsubsection{Network Functions Section}
    \begin{table}[h]
    \centering
    \begin{tabular}{ |p{4cm}|p{10cm}|}
        \hline
        \textbf{Parameter} & \textbf{Description} \\
        \hline
         
         network\_functions & Contains all the VNFs that are handled by the network service. \\
         \hline
         Vnf\_id & Represents a unique identifier within the scope of the NSD \\
         \hline
         Vnf\_vendor & As part of the primary key, the vendor parameter identifies the VNF Descriptor \\
         \hline
         Vnf\_name & As part of the primary key, the name parameter identifies the VNF Descriptor \\
         \hline
         Vnf\_version & As part of the primary key, the version parameter identifies the VNF Descriptor\\
         \hline
         Vnf\_description & It's an optional parameter, a human-readable description of the VNF\\
         \hline
    \end{tabular}
    \caption{Pishahang: Network Functions Section}
    \label{tab:SONATA_NF_section}
 \end{table}

\subsection{Open Source MANO(OSM)}
\label{SecOSM}
OSM is an open source management and orchestration stack in compliant with ETSI NFV information models. OSM architecture splits between resource orchestrators and service orchestrators \cite{de2018network}. Table \ref{tab:OSM_nsd} lists the parameters of NSD schema. \cite{OSMSchemaDocumentation}
    \begin{table}[h]
        \centering
    \begin{tabular}{ |p{4cm}|p{10cm}|}
        \hline
        \textbf{Parameter} & \textbf{Description} \\
        \hline
         
         id &   Identifier for the NSD \\
         \hline
         name & NSD name \\
         \hline
         Short-name &   Short name which appears on the UI \\
         \hline
         vendor &   Vendor of the NSD \\
         \hline
         logo & File path for the vendor specific logo. For example, icons/mylogo.png. The logo should be a part of the network service. \\
         \hline
         description &  Description of the NSD \\
         \hline
         version &  Version of the NSD \\
         \hline
    \end{tabular}
        \caption{OSM: Network Service Descriptor}
    \label{tab:OSM_nsd}
 \end{table}


\section{Virtualized Infrastructure Manager (VIM)}
VIM is one of the three functional blocks specified in the Network Functions Virtualization Management and Orchestration (NFV-MANO) architecture. VIM is responsible for controlling and managing the NFV Infrastructure (NFVI), by provisioning and optimizing the allocation of physical resources to the virtual resources in the NFVI. Performance and error monitoring is also a key role of the VIM. Popular VIMs are discussed in the following sections.

\subsection{OpenStack}
\label{SecOpenStack}
OpenStack\footnote{https://www.openstack.org/} is a community-driven open source cloud resource management platform. Compute, storage, and networking resources in a data center can be provisioned using Application Program Interfaces (APIs) or web dashboard provided by OpenStack component, for instance, NOVA is a component which can provide access to compute resources, such as virtual machines and containers. Network management is enabled by NEUTRON component which handles the creation and management of a virtual networking infrastructure like switches and routers. SWIFT component provides a storage system. By making use of many such components, OpenStack can deliver complex services by utilizing an underlying pool of resources.

\subsection{Kubernetes}
\label{SecKubernetes}
Kubernetes\footnote{https://kubernetes.io/} (K8s) is an open-source platform for automation and management of containerized services, it manages computing, networking, and storage infrastructure. Kubernetes was initially developed by Google and now under Cloud Native Computing Foundation. Kubernetes Architecture consists of (1) Master server components -- it is the control plane of the cluster and act as the gateway for  administrators (2) Node Server Components -- servers which are performing work by using containers that are called nodes, they communicate with the master component for instructions to run the workload assigned to them. Kubernetes provides comprehensive APIs which are used to communicate between the components and with the external user.
